Tables/Graphs for Article

### 2018-01-12 article/draft1.Rnw
combined table 1, removed percentiles table, univariate results table

% Table of categorical predictors
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{10cm}|}
  \hline
  Device category the question pertains to. Categories include: Android/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \hline
  If the question was posted on a weekend or on a weekday \\ \hline
  Whether or not the question's text contains any end punctuation marks (. ? !) \\ \hline
  Whether or not the question's text is in all lower case \\ \hline
  Whether or not the question's title contains at least one word considered to be ``frequently used'' among answered questions \\ \hline
  Whether or not the question's title contains at least one word considered to be ``frequently used'' among unanswered question \\ \hline
  Whether or not the question's title ends in a question mark \\ \hline
  Whether or not the user edited or added information to the question's text after posting it \\ \hline
  Whether or not the user made an effort to solve the problem prior to asking the question \\ \hline
\end{tabular}
\caption{Categorical variables derived}
\label{table:categorical}
\end{table}

% Table of quantitative predictors
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{10cm}|}
  \hline
  Average number of characters in each question's tags (Average tag length) \\ \hline
  Average frequency for all of a question's tags. Frequency defined as the proportion of times a tag appears in all of the data. Questions without tags were assigned a value of 0 (Average tag frequency) \\ \hline
  Number of characters in the question's text (Text length) \\ \hline
  Number of characters in the user-defined device name (Device name length) \\ \hline
  Ratio of the number of line breaks to the number of characters in the question's text (Line break to text length ratio) \\ \hline
\end{tabular}
\caption{Continuous variables derived}
\label{table:continuous}
\end{table}

The data analyzed contained 8,025 questions posted from April 8, 2017 to July 7, 2017 (date of data download). Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date and time the question was posted, and date and time the first answer was received. See Appendix for examples of answered and unanswered questions. Variables derived can be found in Table \ref{table:categorical} and \ref{table:continuous}. See Appendix for more details on variable derivation.

@@

Questions analyzed were restricted to those posted in English. The time until event variable used in survival analysis was defined as the time since posting until a question receives its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the observed download time (questions may receive answers after the download date) \cite{Kleinbaum2011}.

@@

As the probability distribution for response times is unknown, a nonparametric Cox proportional hazards model was developed to predict the survival probability of questions \cite{Moore2010}. To build the model, five-fold cross-validation was used \cite{Rodriguez2010}. Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}. Each predictor was entered into univarite Cox models and strength of association with response times was assessed. Those with partial likelihood ratio test p-values of less than 0.001 were included in the final model. Continuous predictors were entered into univariate Cox models both with and without square root and log transformations to determine the form of the predictor to include in the final model. Univariate analysis was again performed on each continuous predictor to investigate the use of splines. Each predictor, with the transformation found necessary in the previous analysis, was fit to three separate Cox models with restricted cubic splines of three, four, and five knots. AIC statistics were used to determine whether or not to include splines, as well as the optimum number of knots \cite{Harrell2015}. All predictors found to be signficant, along with transformations and splines found to be necessary, were included in the model for cross-validation. No variable selection was used after identifying significant predictors in univariate analysis, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than including all predictors.

In each iteration of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set. To assess prediction performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as the survival time. The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}. Signficant results from this model would indicate high predictive accuracy. The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with predictors, and the log partial likelihood function for the null model without predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model. The p-value for this statistic was calculated from the $chi^2$ distribution \cite{find}. Concordance statistics and Somers' \textit{Dxy} are a measure of the model's discriminative ability. Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter response time also has the higher predicted hazard ratio. Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions. Somers' \textit{Dxy} is the difference between the model's concordance statistic and discordance, 0.5. A Somers' \textit{Dxy} statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \cite{Harrell2015}. These metrics were computed for each iteration on every training and test set. Averages of metrics across training and test sets were evaluated. The final model was then fit to the full data and the same metrics were computed and compared.

Correlations between scaled Schoenfeld residuals, differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that the effect of predictors on hazard does not depend on time \cite{Grambsch1994}. Significant correlations would indicate that a predictor has violated this assumption.

To obtain predicted survival probabilities using the model, the \textit{predictSurvProb} function was used from the pec package in R. This function uses the Cox model and a vector of times to compute predicted survival probabilities.

@@

  Of 8,025 questions in the full data set, \Sexpr{format(nrow(x), big.mark = ",")} were in English (97\% of the full data). Of those questions, \Sexpr{format(answered, big.mark = ",")} (\Sexpr{percentans}}\%) received an answer by the download date. The shortest response time was \Sexpr{shortest} hours. The longest was \Sexpr{format(longest, big.mark = ",")} hours (\Sexpr{longest_d} days). Figure ~\ref{fig:answertimes} shows the distribution of response times for all questions analyzed.

@@

% Table of percentiles 
\begin{table}[!h]
\centering
\begin{tabular}{| l | l |}
  \hline
 \textbf{Percent Answered} & \textbf{Time (hrs)} \\ 
  \hline
  25 & 0.88 \\ 
  50 & 9.16 \\ 
  55 & 18.38 \\ 
  58 & 33.71 \\ 
  60 & 59.47 \\ 
  64 & 683.19 \\ 
   \hline
\end{tabular}
\caption{Kaplan-Meier estimated quantiles of survival time}
\label{table:quantiles}
\end{table}

  Figure ~\ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability curve for all questions in the data. The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was \Sexpr{mean} hours, or \Sexpr{round(mean / 24, 2)} days. The median survival time, the time at which 50\% of the questions in the data received an answer, was \Sexpr{median} hours. Table \ref{table:quantiles} provides additional percentiles of survival time.

% Univariate analysis results
\begin{table}[!htbp]
\centering
\begin{tabular}{| p{5cm} | p{2.75cm} | p{2cm} |}
  \hline
  \textbf{Continuous Predictors} & \textbf{Transformation} & \textbf{p-value} \\ 
  \hline \hline
  \multirow{ 3 }{ 5cm }{ Average tag frequency }
  & Untransformed & 1.270620e-08 \\
  & Log + 1 & 1.186521e-08 \\
  & \textbf{*}Square root & 1.464184e-11 \\ \hline
  \multirow{ 3 }{ 5cm }{ Average tag length }
  & Untransformed & 2.611529e-02 \\ 
  & \textbf{*}Log + 1 & 6.018542e-05 \\
  & Square root & 2.999917e-04 \\ \hline
  \multirow{ 3 }{ 5cm }{ Device name length }
  & Untransformed & 6.530431e-03 \\
  & \textbf{*}Log + 1 & 1.912977e-05 \\
  & Square root & 2.291424e-04 \\ \hline
  \multirow{ 3 }{ 5cm }{ Line break to text length ratio } 
  & Untransformed & 1.398819e-07 \\
  & Log + 1 & 1.092952e-07 \\
  & \textbf{*}Square root & 1.148792e-11 \\ 
  \multirow{ 3 }{ 5cm }{ Text length }
  & Untransformed & 6.947221e-12 \\
  & \textbf{*}Log & 0.000000e+00 \\
  & Square root & 1.110223e-16 \\ \hline \hline
  \multicolumn{ 2 }{ |l| }{ \textbf{ Categorical Predictors } } & \textbf{ p-value } \\ \hline \hline
  \multicolumn{ 2 }{ |l| }{ \textbf{*}Device category } & 0.000000e+00 \\ \hline
  \multicolumn{ 2 }{ |l| }{ \textbf{*}Weekend or Weekday } & 4.123729e-04 \\ \hline
  \multicolumn{ 2 }{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text contained at least one end punctuation mark } & 2.535394e-09 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text is in all lower case } & 1.540030e-07 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & 0.000000e+00 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title ended in a questionmark } & 1.142308e-12 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user edited or added information to the question's text sometime after posting it } & 2.547222e-07 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user had been a member for less than one day before the question was posted } & 0.000000e+00 \\ \hline
  \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & 3.164815e-05 \\ \hline
\end{tabular}
\caption{Univariate analysis results} 
\label{table:univariate_results}
\end{table}

@@

Each training set contained \Sexpr{format(nrow(train1), big.mark = ",")} questions, and each test set contained \Sexpr{format(nrow(test1), big.mark = ",")} questions. Results of univariate analysis performed on one training set are shown in Table \ref{table:univariate_results}. For continuous predictors that contained zeros, one was added to each observation before applying log transformations. All categorical predictors and all continuous predictors marked with an asterisk (*) were entered into the full model.

@@

% Cross-validation metrics
\begin{table}[!htbp]
\centering
\begin{tabular}{| r | r | r | r | r  | r | r | r |}
  \hline
 & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{Concordance} \\ 
  \hline
  \textbf{Training Sets} & 2.027030 & 937.3877 & 0.0000 & 0.1401511 & 0.2683734 & 0.6341867 \\ 
  \textbf{Test Sets} & 1.986844 & 220.8309 & 0.0000 & 0.1400518 & 0.2582790 & 0.6291395 \\
  \textbf{Full Data} & 2.028051 & 1165.0321 & 0.0000 & 0.1394092 & 0.2672884 & 0.6336442 \\ 
   \hline
\end{tabular}
\caption{Performance Metrics} 
\label{table:cv}
\end{table}

@@

% Final model on full data
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{3.5cm} p{4cm}| c | l | c |}
  \hline
 \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{95\% CI} & \textbf{p-value} \\ \hline
  \multirow{ 9 }{ 3.5 cm }{ Device Category } & Apple Product & \hl{0.9346} (0.0476) & & 0.000000e+00 \\ 
  & Camera & -0.3199 (0.0476) & & \\ 
  & Electronics & -0.0138 (0.0904) & & \\ 
  & Game Console & 0.2458 (0.0784) & & \\ 
  & Home & 0.3368 (0.0697) & & \\ 
  & Other & -0.1304 (0.0555) & & \\ 
  & PC & 0.2818 (0.0597) & & \\ 
  & Tablet & -0.1566 (0.0815) & & \\ 
  & Vehicle & 0.4056 (0.0695) & & \\ 
  \hline
  \multicolumn{ 2 }{ |l| }{ Weekend or weekday } & \hl{-0.1334} (0.0331) & & 5.525114e-05 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's text contained at least one end punctuation mark } & 0.0247 (0.0499) & & 6.204270e-01 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's text is in all lower case } & -0.1770 (0.0645) & & 6.065638e-03 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among answered questions } & 0.0475 (0.0422) & & 2.604130e-01 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & \hl{-0.2808} (0.0340) & & 1.110223e-16 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title ended in a questionmark } & 0.2571 (0.0332) & & 9.880985e-15 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user edited or added information to the question's text sometime after posting it } & 0.2983 (0.0857) & & 5.027830e-04 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user had been a member for less than one day before the question was posted } & -0.1069 (0.0364) & & 3.300423e-03 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & -0.0724 (0.0362) & & 4.534803e-02 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Square root of the average tag frequency } & 2.2609 (0.7196) & & 1.679666e-03 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ \multirow{3}{*}{Square root of average tag length} } & -0.0814 (0.0309) & & \\
  & & 0.5945 (0.2661) & & \\
  & & -1.5879 (0.7231) & & \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ \multirow{4}{*}{Log of text length} } & -0.0619 (0.1856) & & \\
  & & -0.5052 (0.8452) & & \\
  & & 2.9957 (4.1706) & & \\
  & & -4.4755 (6.8975) & & \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ \multirow{4}{*}{Log of device name length} } & -0.0488 (0.0714) & & \\
  & & -0.4348 (0.9724) & & \\
  & & 1.2208 (2.3149) & & \\
  & & -1.3199 (2.3255) & & \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ \multirow{2}{*}{Square root of line break to text length ratio} } & -0.0076 (0.4776) & & \\
  & & 0.4345 (0.7265) & & \\ \hline
\end{tabular} 
\caption{Coefficients for predictors in the final model} 
\label{table:coefficients}
\end{table}

>>>>

% Table of derived predictors
\begin{table}[!htbp]
\centering
\begin{tabular}{| p{2cm} | p{10cm} |}
  \hline
  \multirow{9}{2cm}{Categorical Variables} & Device category the question pertains to. Categories include: Android/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \cline{2-2}
  & If the question was posted on a weekend or on a weekday \\ \cline{2-2}
  & Whether or not the question's text contains any end punctuation marks (. ? !) \\ \cline{2-2}
  & Whether or not the question's text is in all lower case \\ \cline{2-2}
  & Whether or not the question's title contains at least one word considered to be ``frequently used'' among answered questions \\ \cline{2-2}
  & Whether or not the question's title contains at least one word considered to be ``frequently used'' among unanswered question \\ \cline{2-2}
  & Whether or not the question's title ends in a question mark \\ \cline{2-2}
  & Whether or not the user edited or added information to the question's text after posting it \\ \cline{2-2}
  & Whether or not the user made an effort to solve the problem prior to asking the question \\ \hline
  \multirow{5}{2cm}{Continuous Variables} & Average number of characters in each question's tags (Average tag length) \\ \cline{2-2}
  & Average frequency for all of a question's tags. Frequency defined as the proportion of times a tag appears in all of the data. Questions without tags were assigned a value of 0 (Average tag frequency) \\ \cline{2-2}
  & Number of characters in the question's text (Text length) \\ \cline{2-2}
  & Number of characters in the user-defined device name (Device name length) \\ \cline{2-2}
  & Ratio of the number of line breaks to the number of characters in the question's text (Line break to text length ratio) \\ \hline
\end{tabular}
\caption{Categorical and Continuous variables derived}
\label{table:variables}
\end{table}

The data analyzed contained 8,025 questions posted from April 8, 2017 to July 7, 2017 (date of data download). Variables in the data included: device name and category, title, text, tags, whether or not the user was a member of iFixit's site for less than one day before the question was posted, date and time the question was posted, and date and time the first answer was received. See Appendix for examples of answered and unanswered questions. Variables derived can be found in Table \ref{table:variables}. See Appendix for more details on variable derivation.

@@

Questions analyzed were restricted to those posted in English. The time until event variable used in survival analysis was defined as the time since posting until a question received its first answer. For questions that did not receive an answer by the download date, time until event values were defined as the time since posting to the time the data was downloaded. Such questions were considered right-censored, meaning that exact answer times for these questions are greater than the observed download time (questions may receive answers after the download date) \cite{Kleinbaum2011}.

@@

As the probability distribution for response times is unknown, a nonparametric Cox proportional hazards model was developed to predict the survival probability of questions \cite{Moore2010}. To build the model, five-fold cross-validation was used \cite{Rodriguez2010}. Univariate analysis, performed on one training set, was used to identify variables to include in the final predictive Cox model \cite{Hammermeister1979}. Each predictor was entered into univariate Cox models and strength of association with response times was assessed. Those with partial likelihood ratio p-values of less than 0.001 were included in the final model.  Continuous predictors were entered into univariate Cox models both with and without square root and log transformations to determine the form of the predictor to include in the final model. Univariate analysis was again performed on each continuous predictor to investigate the use of splines. Each predictor, with the transformation found necessary in the previous analysis, was fit to three separate Cox models with restricted cubic splines of three, four, and five knots. AIC statistics were used to determine whether or not to include splines, as well as the optimum number of knots \cite{Harrell2015}. All predictors found to be signficant, along with transformations and splines found to be necessary, were included in the model for cross-validation. No variable selection was used after identifying significant predictors in univariate analysis, as \cite{Harrell2015} determined that reducing the number of predictors in the model decreased predictive accuracy more so than including all predictors.

In each iteration of cross-validation, the full model was built on the training set and used to generate predicted hazard ratios on the corresponding test set. To assess prediction performance, predicted hazard ratios were entered into separate Cox models as the single quantitative predictor with response times as survival time. The resulting Nagelkerke's $R^2$ statistic, concordance statistic, Somers' \textit{Dxy}, partial likelihood ratio and p-value, were assessed as indicators of the model's performance \cite{Chen}. Signficant results from this model would indicate high predictive accuracy. The partial likelihood ratio assessed is a ratio of the log partial likelihood function evaluated at the parameter estimates, equivalent to a goodness of fit measure of the model with predictors, and the log partial likelihood function for the null model without predictors and only the baseline hazard function, equivalent to a goodness of fit measure for the null model. The p-value for this statistic was calculated from the $chi^2$ distribution \cite{Oakes1981}. Concordance statistics and Somers' \textit{Dxy} are a measure of the model's discriminative ability. Concordance is defined as the probability that for any two randomly chosen questions, the question with the shorter response time also has the higher predicted hazard. Concordance statistics close to 1 indicate high discriminative ability, while statistics close to 0.5 indicate discordance, or random predictions. Somers' \textit{Dxy} is the difference between the model's concordance statistic and discordance, 0.5. A Somers' \textit{Dxy} statistic of 0 indicates random predictions, while a statistic equal to 1 indicates perfect predictions \cite{Harrell2015}. These metrics were computed for each iteration on every training and test set. Averages of metrics across training and test sets were evaluated. The final model was then fit to the full data and the same metrics were computed and compared.

Correlations between scaled Schoenfeld residuals, differences between observed and expected predictor values for questions that received answers, and a function of time, were examined to assess the proportional hazards assumption that the effect of predictors on hazard does not depend on time \cite{Grambsch1994}. Significant correlations would indicate a predictor has violated this assumption.

To compute predicted survival probabilities using the model, the \textit{predictSurvProb} function was used from the pec package in R. This function uses the Cox model and a vector of times to compute predicted survival probabilities.

@@

  Of 8,025 questions in the full data, \Sexpr{format(nrow(x), big.mark = ",")} were in English (97\% of the full data). Of those questions, \Sexpr{format(answered, big.mark = ",")} (\Sexpr{percentans}}\%) received an answer by the download date. The shortest response time was \Sexpr{shortest} hours. The longest was \Sexpr{format(longest, big.mark = ",")} hours (\Sexpr{longest_d} days). Figure ~\ref{fig:answertimes} shows the distribution of response times for all questions analyzed.

@@

  Figure ~\ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability curve for all questions in the data. The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was \Sexpr{mean} hours, or \Sexpr{round(mean / 24, 2)} days. The median survival time, the time at which 50\% of the questions in the data received an answer, was \Sexpr{median} hours.

% % Univariate analysis results
% \begin{table}[!htbp]
% \centering
% \begin{tabular}{| p{5cm} | p{2.75cm} | p{2cm} |}
%   \hline
%   \textbf{Continuous Predictors} & \textbf{Transformation} & \textbf{p-value} \\ 
%   \hline \hline
%   \multirow{ 3 }{ 5cm }{ Average tag frequency }
%   & Untransformed & 1.270620e-08 \\
%   & Log + 1 & 1.186521e-08 \\
%   & \textbf{*}Square root & 1.464184e-11 \\ \hline
%   \multirow{ 3 }{ 5cm }{ Average tag length }
%   & Untransformed & 2.611529e-02 \\ 
%   & \textbf{*}Log + 1 & 6.018542e-05 \\
%   & Square root & 2.999917e-04 \\ \hline
%   \multirow{ 3 }{ 5cm }{ Device name length }
%   & Untransformed & 6.530431e-03 \\
%   & \textbf{*}Log + 1 & 1.912977e-05 \\
%   & Square root & 2.291424e-04 \\ \hline
%   \multirow{ 3 }{ 5cm }{ Line break to text length ratio } 
%   & Untransformed & 1.398819e-07 \\
%   & Log + 1 & 1.092952e-07 \\
%   & \textbf{*}Square root & 1.148792e-11 \\ \hline
%   \multirow{ 3 }{ 5cm }{ Text length }
%   & Untransformed & 6.947221e-12 \\
%   & \textbf{*}Log & 0.000000e+00 \\
%   & Square root & 1.110223e-16 \\ \hline \hline
%   \multicolumn{ 2 }{ |l| }{ \textbf{ Categorical Predictors } } & \textbf{ p-value } \\ \hline \hline
%   \multicolumn{ 2 }{ |l| }{ \textbf{*}Device category } & 0.000000e+00 \\ \hline
%   \multicolumn{ 2 }{ |l| }{ \textbf{*}Weekend or Weekday } & 4.123729e-04 \\ \hline
%   \multicolumn{ 2 }{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text contained at least one end punctuation mark } & 2.535394e-09 \\ \hline
%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's text is in all lower case } & 1.540030e-07 \\ \hline
%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among answered questions } & 7.639738e-05 \\ \hline
%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & 0.000000e+00 \\ \hline
%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the question's title ended in a questionmark } & 1.142308e-12 \\ \hline
%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user edited or added information to the question's text sometime after posting it } & 2.547222e-07 \\ \hline
%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user had been a member for less than one day before the question was posted } & 0.000000e+00 \\ \hline
%   \multicolumn{2}{ |p{7.75cm}| }{ \textbf{*}Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & 3.164815e-05 \\ \hline
% \end{tabular}
% \caption{Univariate analysis results} 
% \label{table:univariate_results}
% \end{table}

@@

Each training set contained \Sexpr{format(nrow(train1), big.mark = ",")} questions, and each test set contained \Sexpr{format(nrow(test1), big.mark = ",")} questions. Univariate analysis performed on one training set indicated that all cateogorical predictors were signficant with partial likelihood ratio p-values of less than 0.001. All continuous predictors, except for device length and average tag length, also resulted in univariate p-values of less than 0.001. Applying either square root or log transformations to continuous variables resulted in univariate p-values of less than 0.001. For continuous predictors that contained zeros, one was added to each observation before applying the log transformation. The following transformations were applied to continuous variables: square root transformation of average tag frequency, log plus 1 transformation of average tag length, log plus 1 transformation of device name length, square root transformation of line break to text length ratio, and log transformation of text length. All categorical predictors and all continuous predictors with necessary transformations were retained for the full model.

@@

% Cross-validation metrics
\begin{table}[!htbp]
\centering
\begin{tabular}{| r | r | r | r | r  | r | r | r |}
  \hline
 & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{Concordance} \\ 
  \hline
  \textbf{Training Sets} & 2.027030 & 937.3877 & 0.0000 & 0.1401511 & 0.2683734 & 0.6341867 \\ 
  \textbf{Test Sets} & 1.986844 & 220.8309 & 0.0000 & 0.1400518 & 0.2582790 & 0.6291395 \\
  \textbf{Full Data} & 2.028051 & 1165.0321 & 0.0000 & 0.1394092 & 0.2672884 & 0.6336442 \\ 
   \hline
\end{tabular}
\caption{Performance Metrics. HR: Hazard Ratio, LR: Partial Likelihood Ratio} 
\label{table:cv}
\end{table}

@@

% Final model on full data
\begin{table}[!htbp]
\centering
\begin{tabular}{|p{3cm} p{4cm}| c | c |}
  \hline
 \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{p-value} \\ \hline
  \multirow{ 9 }{ 3 cm }{ Device Category } & Apple Product & 0.9346 (0.0476) & <0.0001 \\ 
  & Camera & -0.3199 (0.0476) & \\ 
  & Electronics & -0.0138 (0.0904)  & \\ 
  & Game Console & 0.2458 (0.0784)  & \\ 
  & Home & 0.3368 (0.0697) &  \\ 
  & Other & -0.1304 (0.0555)  & \\ 
  & PC & 0.2818 (0.0597) &  \\ 
  & Tablet & -0.1566 (0.0815)  & \\ 
  & Vehicle & 0.4056 (0.0695)  & \\ 
  \hline
  \multicolumn{ 2 }{ |l| }{ Weekend or weekday } & -0.1334 (0.0331)  & <0.0001 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's text contained at least one end punctuation mark } & 0.0247 (0.0499) & 0.6127 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's text is in all lower case } & -0.1770 (0.0645) &  0.0060 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among answered questions } & 0.0475 (0.0422) &  0.2596 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title contains terms considered to be frequently used among unanswered questions } & -0.2808 (0.0340)  & <0.0001 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the question's title ended in a questionmark } & 0.2571 (0.0332) &  <0.0001 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user edited or added information to the question's text sometime after posting it } & 0.2983 (0.0857)  & 0.0005 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user had been a member for less than one day before the question was posted } & -0.1069 (0.0364)  & 0.0031 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Whether or not the user made an effort to solve the problem on their own, prior to asking the question } & -0.0724 (0.0362)  & 0.0448 \\ \hline
  \multicolumn{ 2 }{ |p{7.5cm}| }{ Square root of the average tag frequency } & 2.2609 (0.7196)  & 0.0020 \\ \hline
\end{tabular} 
\caption{Coefficients for predictors in the final model.Continous predictors with restricted cubic splines are not shown. } 
\label{table:coefficients}
\end{table}
